01 - Simulate data

### 2023-11-26 scripts/01_sim_data.qmd
simulate data2

>>>>

```{r}
#| label: eud
# https://mycurvefit.com

x <- 1:9

y_esi <- rep(2.25, 9)
y_esu <- rep(2, 9)
y_esa <- rep(1.5, 9)

y_es0i <- 2 + (-0.3 - 2)/(1 + (x/2)^2.5)
y_es0u <- 1.6 + (-4 - 1.6)/(1 + (x/0.5)^1.5)
y_es0a <- rep(0, 9)

y_es1i <- 2 + (0.9 - 2)/(1 + (x/2)^2.5)
y_es1u <- 1.5 + (1 - 1.5)/(1 + (x/2)^2.5)
y_es1a <- rep(1.25, 9)
```

```{r}
#| label: eud-plot

tibble(
  time = rep(x, 9),
  eud = c(y_esi, y_esu, y_esa, y_es0i, y_es0u, y_es0a, y_es1i, y_es1u, y_es1a),
  group = rep(c("es", "es_0", "es_1"), each = 9*3),
  vowel = rep(rep(c("i", "u", "a"), each = 9), 3)
) %>%
  ggplot(aes(time, eud, colour = vowel)) +
  geom_point(size = 3) +
  facet_grid(cols = vars(group))
```

```{r}

```
